Understanding Complex Patterns in Social, Geographic, and Economic Inequities in COVID-19 Mortality at the County Level in the US Using Generalized Additive Models

### 2022-12-01 manuscript/manuscript.rmd
A is for the strictly parametric terms
The definition of  $\mathbf{A_i}$ given in the manuscript is incorrect. **A** is the model matrix for the strictly parametric terms (i.e terms one might include in a LM or GLM). In general non-parametric is a bit of a misnomer, as all terms in the GAM as you (and Simon) define it are parametric once we've formed the basis expansion(s) for any smooth terms in the model. The distinction between what is and is not parametric gets complicated as models of this form:

```r
m <- gam(y ~ x1 * f1 + bs(x2) + s(x3) + te(x4, x5), data = df, method = "REML")
```

are

Generalized additive models (GAMs) improve upon generalized linear models by
allowing for the fitting of smooth functions that transform the $x$ variables.
This is a convenient means to include nonlinear relationships between the
outcome and predictor variables. Whereas a generalized linear model may look like 
$$ g(\mu_i) = \beta_0 + \beta_1 x_{i1} + \beta_2 x_{i2} + \beta_3 x_{i3} ...$$ 
a generalized additive model could look like 
$$ g(\mu_i) = \mathbf A_i \mathbf \theta + f_1(x_{i1}) + f_2(x_{i2}) + f_3(x_{i3}, x_{i4}) + \dots$$
where $\mu_i \equiv \mathbb E(Y_i)$, $\mathbf A_i$ is a row of the model matrix 
for any strictly non-parametric model components, $\mathbf \theta$ is the corresponding
parameter vector, and the $f_j$ are smooth functions of the covariates $x_k$ [@wood_generalized_2017].

>>>>

Generalized additive models (GAMs) improve upon generalized linear models by
allowing for the fitting of smooth functions that transform the $x$ variables.
This is a convenient means to include nonlinear relationships between the
outcome and predictor variables. Whereas a generalized linear model may look like 
$$ g(\mu_i) = \beta_0 + \beta_1 x_{i1} + \beta_2 x_{i2} + \beta_3 x_{i3} ...$$ 
a generalized additive model could look like 
$$ g(\mu_i) = \mathbf A_i \mathbf \theta + f_1(x_{i1}) + f_2(x_{i2}) + f_3(x_{i3}, x_{i4}) + \dots$$
where $\mu_i \equiv \mathbb E(Y_i)$, $\mathbf A_i$ is a row of the model matrix 
for any strictly parametric model components, $\mathbf \theta$ is the corresponding
parameter vector, and the $f_j$ are smooth functions of the covariates $x_k$ [@wood_generalized_2017].
